---
title: "Tidy Evaluation"
author: "sid"
date: "15 February 2018"
output: html_document
---

## Learning tidy evaluation from hadley's "Advanced R" book.

```{r, echo=FALSE, eval=FALSE}
x <- seq(0, 2 * pi, length = 100)
sinx <- sin(x)
plot(x, sinx, type = "l")
```

Going back to the chapter on "Environments" since it's a pre-requisite to understand NSE.

Download the followining library - *"pryr"*

```{r, echo=FALSE, eval=FALSE}
install.packages("pryr")
library("pryr")
```
 Important concepts about an environment:
 
- An environment is a name-object binding.
- All environment have parents except the empty environment.
- The parent of an environment is the las package thatw as loaded by library().
- All the names in an environment are unique.
- The names in an environment are not ordered.
- Environmenta have reference semantics. 

There are four types of environments:

- Global environment, the one in which we nomally work **globalenv()**. The parent of the 
  global environment is the package that we last loaded with library() or require().
- Base environment - **baseenv()** -is the environment of the base package. It's parent is the
  empty environment.
- The **emptyenv()** is the utimate ancestor of all environments and the only one without a parent.
- The **environment()** is the current environment.

**search()** lists all parents of the global environment.It contains one environment for each 
attached package and any other attached objects.


```{r, echo=TRUE, eval=TRUE, include=TRUE}
library("pryr")
search()
as.environment("package:pryr")

```
To create an an environment manually we use new.env(). To list its bindings we use ls() and to see
its parent environment we use parent.env()

```{r, echo=TRUE, eval=TRUE, include=TRUE}
e <- new.env()
# the default parent provided by new.env() is environment from 
# which it is called - in this case that's the global environment.
ls(e)
parent.env(e)
```
In order to modify bindings in a environment we add components like we do in a list.

```{r, echo=TRUE, eval=TRUE}
e$a <- 1
e$b <- 2
ls(e)
e$a
```

By default, ls() only shows elements whose name does not start with ..Use all.names=TRUE to show all bindings in an environment.

```{r}
e$.a <- 2
ls(e)
ls(e, all.names=TRUE)
```

Another useful way to view the environment is with ls.str(). Use the all.names=TRUE argument. It is better than str() since it shows all the components of the environment.

```{r}
str(e, all.names=TRUE)
ls.str(e, all.names = TRUE)
```

Given a name, we can extract the value to which it is bound by using $, [[]], get()
```{r}
e$c <- 3
e$c
e[["c"]]
get("c", envir = e)
```

Use rm() to delete a binding.

```{r}
e <- new.env()

e$a <- 1
e$b <- NULL

ls(e, all.names = TRUE)
rm("a", envir = e)
ls(e)
```